---
title: "How I am structuring my review paper"
subtitle: ": Towards a Systematic Review"  
author: "Hyesop Shin"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_dark(base_color = "#cbf7ed")
```

class: inverse, top, left

Temporary Title

<br><br>

# Factors Negatively affecting the Participation of Geographic Crowdsourcing Projects: a Systematic Review


---

# Motivation

-  Why do we see biases in participatory mapping projects?
 
- If so, what are the main factors associated with the bias?

---

# Motivation for a Systematic Review


- Several papers have investigated possible factors that hinder the participation in crowdsourced mapping in their VGI projects

- Most empirical studies have extensive questions which can be less generalisable

- To our knowledge, none of the published reviews identified or analysed the available evidence from a strict systematic approach

---

# Advantages of a Systematic Review
- To improve decision that are maximally informed and minimally biased
- The transparency of the selection criteria is a safe bet with academic markers and journal peer reviewers ⇒ “how and why were the studies included or excluded?”
- Far less stressful and far more manageable


---

# Research Objective and Questions

### Objective
- To review and analyse the main factors that underlie a major barrier for Public VGI projects

### Research Questions
- What factors are associated with the under-represent of participation in VGI projects?
- Are there other non-demographic factors that can hinder VGI projects which are not revealed yet?


---

# A PRISMA Guideline

